Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 raspi_journal.tex
TSNC editing and removing unnecesary sections
Wrote on testbed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize\ttfamily,
  breaklines=true,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  %keywordstyle=\color{blue},       % keyword style
  language=Bash,                 % the language of the code
  otherkeywords={*,...},           % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  %stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  title=\lstname,                  % show the filename of files included with \lstinputlisting; also try caption instead of title
  xleftmargin=5mm,
  xrightmargin=5mm,
  columns=flexible
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize\ttfamily,
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  %commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  %keywordstyle=\color{blue},       % keyword style
  %language=Bash,                 % the language of the code
  otherkeywords={*,...},           % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  %stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  title=\lstname,                  % show the filename of files included with \lstinputlisting; also try caption instead of title
  xleftmargin=5mm,
  xrightmargin=5mm,
  columns=flexible
}

### 2016-06-01 testbed.tex
Wrote on testbed

\begin{lstlisting}[frame=single]  % Start your code-block
IMAGE="raspbian_lite-2016-05-31/2016-05-27-raspbian-jessie-lite"
WORKDIR="${HOME}/Raspbian"
cd ${WORKDIR}
wget http://downloads.raspberrypi.org/raspbian_lite/images/${IMAGE}.zip
unzip ${IMAGE}
\end{lstlisting}
\FloatBarrier

>>>>

Open a terminal, and then...

hashmark (#) means to perform operation as root, dollar (\$) means to perform operation as user

%\begin{lstlisting}[caption=Define variable]  % Start your code-block
\begin{lstlisting}[]  % Start your code-block

$ export IMAGE="2016-05-27-raspbian-jessie-lite"
$ export WORKDIR="${HOME}/Raspbian"
\end{lstlisting}
\FloatBarrier

%\begin{lstlisting}[caption=Download and unpack image]  % Start your code-block
\begin{lstlisting}[]  % Start your code-block

$ mkdir -p ${WORKDIR}
$ cd ${WORKDIR}
$ wget http://downloads.raspberrypi.org/raspbian_lite/images/raspbian_lite-2016-05-31/${IMAGE}.zip
$ unzip ${IMAGE}.zip
\end{lstlisting}
\FloatBarrier

%\begin{lstlisting}[caption="Check out the image"]  % Start your code-block
\begin{lstlisting}[]  % Start your code-block

$ fdisk -lu ${IMAGE}.img
Disk 2016-05-27-raspbian-jessie-lite.img: 1.3 GiB, 1387266048 bytes, 2709504 sectors
Units: sectors of 1 * 512 = 512 bytes
Sector size (logical/physical): 512 bytes / 512 bytes
I/O size (minimum/optimal): 512 bytes / 512 bytes
Disklabel type: dos
Disk identifier: 0x6fcf21f3

Device                               Boot  Start     End Sectors  Size Id Type
2016-05-27-raspbian-jessie-lite.img1        8192  137215  129024   63M  c W95 FAT32 (LBA)
2016-05-27-raspbian-jessie-lite.img2      137216 2709503 2572288  1.2G 83 Linux
\end{lstlisting}
\FloatBarrier

We see that the boot and root partitions starts at sector 8192 and 137216 respectivly.
We also notice that each sector is 512 bytes.

Mount root partition:
%\begin{lstlisting}[caption="Mount the root partition"]  % Start your code-block
\begin{lstlisting}[]  % Start your code-block

$ export ROOTDIR="${WORKDIR}/root"
$ mkdir -p ${ROOTDIR}
# mount -o loop,offset=$((137216*512)) ${IMAGE}.img ${ROOTDIR}
\end{lstlisting}
\FloatBarrier

Mount boot partition:
%\begin{lstlisting}[caption="Mount boot partition"]  % Start your code-block
\begin{lstlisting}[]  % Start your code-block

# mount -o loop,offset=$((8192*512)) ${IMAGE}.img ${ROOTDIR}/boot
\end{lstlisting}
\FloatBarrier
